### 2023-06-02 python_excel_ite.tex
describing modeling notebooks

\section{The modeling notebooks}
\subsection{Notebook 1: Modeling and data tables}
\subsection{Notebook 2: Goal seek}
\subsection{Notebook 3: Monte-Carlo simulation}

>>>>

The "Excel with Python" module is comprised of three submodules.

\section{The modeling notebooks}

The first focuses on building a simple what-if model and doing sensitivity analysis much like one would do using Excel's Data-Table functionality. The next submodule explores the creation and use of goal seeking capability so that we can do things like finding the break-even point in our model.

\subsection{Notebook 1: Modeling and data tables}
\subsection{Notebook 2: Goal seek}
\subsection{Notebook 3: Monte-Carlo simulation}
